Title Goes Here

### 2024-05-06 analysis/paper/paper.qmd
methods over time

@@

# explore trends over time. put a point on the max year
jobdata_method_year_tally <-
  jobdata_method_year %>%
  # exclude those with <20 ads
  filter(!name %in% c("Material culture analysis"
  )) %>%
  group_by(year_ad_posted,
           name) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

jobdata_method_year_tally_max <-
  jobdata_method_year_tally %>%
  group_by(
    name ) %>%
  filter(prop == max(prop))

# how many times each topic mentioned?
jobdata_method_year_tally_max %>%

  ggplot() +
  aes(reorder(name, n),
      n)+
  geom_col() +
  xlab("") +
  theme_minimal() +
  coord_flip()

@@

>>>>

library(googlesheets4)
library(stringi)
1

@@

# explore trends over time. put a point on the max year
jobdata_method_year_tally <-
  jobdata_method_year %>%
  # exclude those with <20 ads
  filter(!name %in% c("Material culture analysis",
                      "Ceramic analysis"
  )) %>%
  group_by(year_ad_posted,
           name) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

@@

view(jobdata)
```
